\documentclass{article}

\usepackage{pandekten}

\title{Homotopy}
\author{Ch\=an Taku}

\begin{document}

\maketitle

% \bibliographystyle{plain}
% \bibliography{main}

\section{Vergleichen: Field Theory and Covering}

In the following, $f: P \rightarrow X$ is a universal cover of $X$.
All field extensions are algebraic unless otherwise stated.

\subsection{Covering Spaces}

\begin{definition}{Orbit Space}{orbit_space}
    Input:
    \begin{itemize}
        \item $G$ a group.
        \item $Y$ a topological space.
        \item $G$ acts on $Y$.
    \end{itemize}
    $G\backslash Y$ is a topological space, where
    \begin{itemize}
        \item $Y$ as a set is given by the set of orbits the action, and
        \item the topology on $Y$ is the finest topology such that the natural map $Y\rightarrow G\backslash Y$ is continuous.
    \end{itemize}
\end{definition}

\begin{definition}{Properly Discontinuous Action}{properly_discontinuous_action}
    Input:
    \begin{itemize}
        \item $G$ is a topological group.
        \item $Y$ is a topological space.
        \item $G$ acts on $Y$ continuously.
    \end{itemize}
    The action is properly discontinuous if for all $y\in Y$, there is an open set $V$ containing $y$ such that for all $g_1,g_2\in G$, $g_1 V \cap g_2 V = \varnothing$.
\end{definition}

\begin{theorem}{Covering by Properly Discontinuous Action}{covering_by_properly_discontinuous_action}
    Input:
    \begin{itemize}
        \item $G$ is a topological group.
        \item $Y$ is a connected topological space.
        \item $G$ acts properly discontinuously on $Y$.
    \end{itemize}
    The natural map $\rho:Y\rightarrow G\backslash Y$ makes $Y$ a cover of $G\backslash Y$.
\end{theorem}

\begin{theorem}{Covering Automorphism is Free}{covering_automorphism_is_free}
    A automorphism of a covering $Y\rightarrow X$ is either trivial or has no fixed points.
\end{theorem}

\begin{theorem}{Covering Automorphism is Properly Discontinuous}{covering_automorphism_is_properly_discontinuous}
    If $Y\rightarrow X$ is connected, then the action of $\operatorname{Aut}(Y/X)$ on $Y$ is properly discontinuous.
\end{theorem}

\subsection{Universal Cover}

\begin{theorem}{Path Lift}{path_lift}
    Let $\rho:(Y,y) \rightarrow (X,x)$ be a cover.
    For any path $f:[0,1]\rightarrow X$ with $f(0) = 1$, there exists a unique lift $f':[0,1]\rightarrow Y$ such that $f'(0) = y$ and $\rho\circ f' = f$.
\end{theorem}

\begin{theorem}{Monodromy Action on Finite Separable Extensions}{monodromy_action_on_finite_separable_extensions}
    {\color{red}TODO}
\end{theorem}

\begin{definition}{Monodromy Action}{monodromy_action}
    Input:
    \begin{itemize}
        \item $\rho:Y\rightarrow X$ is a covering.
        \item $x\in X$.
    \end{itemize}
    The monodromy action is an action of $\pi(X,x)$ on $\rho^{-1}(x)$ defined by
    \[ \phi \cdot y = f'(1) \]
    where $f$ is any loop in the equivalence class of $\phi$ such that $f'(0) = y$.
\end{definition}

\begin{theorem}{Galois Group and Fundamental Group}{galois_group_and_fundamental_group}
    Given a space $(X,x)$,
    \[ \operatorname{Gal}(\tilde{X}_x/X)^\mathrm{op} \cong \pi(X,x). \]
\end{theorem}

Let $X$ be a space and $x\in X$ be a point.
$\operatorname{Fib}_x$ is a functor
\begin{itemize}
    \item from the category of covers of $X$,
    \item to the category of sets equipped with a left $\pi_1(X,x)$ action
\end{itemize}
defined by sending
\begin{itemize}
    \item a cover $p:Y\rightarrow X$,
    \item to the fiber $p^{-1}(x)$.
\end{itemize}

\begin{theorem}{Equivalence of Covering Spaces with Sets}{equivalence_of_covering_spaces_with_sets}
    Let $X$ be a connected and locally simply connect topological space, and $x\in X$ a base point.
    The functor $\operatorname{Fib}_x$ induces an equivalence of the category of covers of $X$ with the category of left $\pi_1(X,x)$-sets.
\end{theorem}

\begin{theorem}{Equivalence of Covering Spaces with Sheaves}{equivalence_of_covering_spaces_with_sheaves}
    Let $X$ be a topoogical space.
    The following two categories are equivalent:
    \begin{itemize}
        \item the category of covers of $X$, and
        \item locally constant sheaves on $X$.
    \end{itemize}
\end{theorem}

\begin{longtable}{>{\raggedright\arraybackslash}m{.45\linewidth}>{\raggedright\arraybackslash}m{.45\linewidth}}
\toprule
Field & Covering \\
\midrule
& $\pi_1(X) \leftrightarrow f^{-1}(x)$ \\
Extension homomorphism & Covering morphism \\
\midrule
{Galois extension: $\operatorname{Aut}(E/F)$ fixes exactly $F$} & \\
Separable \\
Minimal polynomials split \\
Separable closure $\Leftrightarrow$ maximal Galois extension \\
Absolute Galois group $\operatorname{Gal}(K/k)$ \\
\midrule
Galois group $\operatorname{Aut}(E/F)$ permutes roots of polynormals over the base field & Covering automorphism group $\operatorname{Aut}(Y/X)$ permutes the fibers of the cover  \\
Galois extension: $\operatorname{Gal}(E/F)$ acts transitively on the set of roots of any irreducible polynomial & Galois covering: every fiber is permuted transitively by the group \\
\midrule
Galois correspondence: $\operatorname{Gal}(L/F)$ & Galois correspondence: $\operatorname{Gal}(Y/X)$ \\
$E/F \leftrightarrow \operatorname{Gal}(L/E)$ & $Z/X \leftrightarrow \operatorname{Gal}(Y/Z)$ \\
$L^H \leftrightarrow H$ & $(H\backslash Y\rightarrow X) \leftrightarrow H$ \\
$L/E$ is Galois & $Y/Z$ is Galois if $Y\xrightarrow{\exists f} Z$ \\
$E/F$ is Galois if $H \trianglelefteq G$ & $Z/X$ is Galois if $H \trianglelefteq G$ \\
$\operatorname{Gal}(E/F) \cong G/H$ & $\operatorname{Gal}(Z/X) \cong G/H$ \\
\midrule
Absolute Galois group & Fundamental group \\
Separable closure (is Galois) & Universal cover (is Galois) \\
& Covering of $X$ with automorphism group $H$ $\leftrightarrow$ subgroup $H$ of $\pi_1$ \\
& Galois covering of $X$ $\leftrightarrow$ normal subgroup of $\pi_1$ \\
\midrule
Every finite group is a Galois group & Every group is a fundamental group \\
Galois action: $\operatorname{Gal}$ acting on $\operatorname{Hom}_F(E,\overline{F})$ & Monodromy action: $\pi_1$ acting on $p^{-1}(x)$ \\
$E \mapsto \operatorname{Hom}_F(E,\overline{F})$ & $Y\mapsto \operatorname{Hom}_X(\tilde{X}_x,Y) \cong \operatorname{Fib}_x(Y)$ \\
\bottomrule
\end{longtable}

\begin{example}{Homotopic Spaces Have Different Universal Covers}{homotopic_spaces_with_different_covers}
    The universal cover of $S^1$ is $\mathbb{R}$ while the universal cover of $\mathbb{C}\backslash\qty{0}$ is $\mathbb{C}$ given by $z\mapsto e^z$.
\end{example}

\section{Application to Complex Analysis}

Little Picard theorem and unsolvability of quintic equations.

\end{document}
