\documentclass{article}

\usepackage{pandekten}

\title{Allgemein}
\author{Ch\=an Taku}

\begin{document}

\maketitle

\section{Homotopy}

\begin{definition}{Homotopic Equivalent Spaces}{homotopic_equivalent_spaces}
    $(X,x_0)$ is homotopic equivalent to $(Y,y_0)$ if there is a pointed continuous map $f:(X,x_0) \rightarrow (Y,y_0)$ and $g:(Y,y_0) \rightarrow (X,x_0)$, such that both $f\circ g$ and $g\circ f$ are both homotopic to the identity maps.
\end{definition}

\begin{proposition}{Homotopic Equivalent Spaces Have Identical $\pi_1$}{homotopic_equivalent_spaces_have_identical_pi_1}
    If $(X,x_0)$ is homotopic equivalent to $(Y,y_0)$ then $\pi_1(X,x_0) \cong \pi_1(Y,y_0)$.
\end{proposition}

\begin{theorem}{Seifert-Van-Kampen Theorem}{seifert-van-kampen-theorem}
    Input:
    \begin{itemize}
        \item $U$ and $V$ are topological spaces.
        \item $x_0\in U\cap V$.
        \item $U$, $V$, and $U\cap V$ are pathwise connected.
    \end{itemize}
    Then $\pi_1(U\cup V,x_0)$ may be obtained with $\pi_1(U,x_0)$ and $\pi_1(V,x_0)$ as the free product with amalgamation
    \[ \pi_1(U\cup V) = \pi_1(U) *_{\pi_1(U_1\cap U_2)} \pi_1(V). \]
\end{theorem}

\begin{corollary}{Simply Connected Glue}{simply_connected_glue}
    Input:
    \begin{itemize}
        \item $U$ and $V$ are topological spaces.
        \item $x_0\in U\cap V$.
        \item $U\cap V$ is simply connected.
    \end{itemize}
    Then
    \[ \pi_1(U\cup V, x_0) = \pi_1(U,x_0) * \pi_1(V,x_0), \]
    where $*$ denotes the free product.
\end{corollary}

\section{Poincar\'e Duality}

\begin{theorem}{Orientable Manifold has Disconnected Orientation Cover}{orientable_manifold_has_disconnected_orientation_cover}
    If $M$ is a connected $n$-manifold, then $M$ is orientable if and only if $\tilde{M}$ is not connected, where $\tilde{M}$ is the orientation cover of $M$.
\end{theorem}

\begin{theorem}{Properties of Compact Connected}{properties_of_compact_connected}
    If $M$ is a compact connected $n$-manifold, then all of the following hold.
    \begin{itemize}
        \item $H_i(M) = 0$ for all $i>n$.
        \item If $M$ is orientable then
        \[ H_n(M) \rightarrow H_n(M,M-p) \cong \mathbb{Z} \]
        is an isomorphism for all $p\in M$.
        \item If $M$ is not orientable, then $H_n(M)=0$.
    \end{itemize}
\end{theorem}

A generator for $H_n(M;\mathbb{Z})$ is called a fundamental class.
\begin{corollary}{Existence Fundamental Class}{existence_of_fundamental_class}
    A fundamental class for a connected manifold $M$ exists if and only if $M$ is compact and orientable.
\end{corollary}

\begin{lemma}{Section of Orientation to Homology Class}{section_of_orientation_to_homology_class}
    Let $M$ be an $n$-manifold, and $A\subset M$ be a compact set.
    \begin{itemize}
        \item $H_i(M,M-A) = 0$ for all $i>n$.
        \item If $p\mapsto \alpha_p$ is a section of
        \[ M_{\mathbb{Z}} \rightarrow M, \]
        then there exists a unique $\alpha\in H_n(M,M-A)$ such that $\alpha$ in $H_n(M,M-p)$ coincides with $\alpha_p$.
    \end{itemize}
\end{lemma}

\begin{theorem}{Poincar\'e Duality}{poincare_duality}
    If $M$ is a connected orientable manifold, then
    \[ H^k(M) \cong H_{n-k}(M). \]
\end{theorem}

% \bibliographystyle{plain}
% \bibliography{main}

\end{document}
