\documentclass{ctexart}

\usepackage{pandekten}
\usepackage{dashrule}

\makeatletter
\newcommand*{\shifttext}[1]{%
  \settowidth{\@tempdima}{#1}%
  \hspace{-\@tempdima}#1%
}
\newcommand{\plabel}[1]{%
\shifttext{\textbf{#1}\quad}%
}
\newcommand{\prule}{%
\begin{center}%
\hdashrule[0.5ex]{.99\linewidth}{1pt}{1pt 2.5pt}%
\end{center}%
}

\makeatother

\newcommand{\minusbaseline}{\abovedisplayskip=0pt\abovedisplayshortskip=0pt~\vspace*{-\baselineskip}}%

\setlength{\parindent}{0pt}

\title{Assignment 2}
\author{Ze (Zack) Chen}

\begin{document}

\maketitle

\plabel{$\blacktriangleright$}%
かくの如き名族は、\\
Such renowned families\\
當時の政治上の位置から殆ど超越して居る。\\
have almost exceeded the political position then.

\vspace{1em}
\plabel{$\blacktriangleright$}%
即ち當時の政治は貴族全體の專有ともいふべきものであつて、\\
That is to say, even though the thing exists that it should be said that the politics then was a exclusive belonging of the whole lords, and\\
貴族でなければ高い官職に就く事が出來なかつたが、\\
if (one was) not a lord, the thing that (he) assume a high office position was impossible, but,\\
しかし第一流の貴族は必ず天子宰相になるとも限らない。
(however,) it is not necessary that the first-tier lords absolutely become the Son of Heaven or the Chancellor either.

\vspace{1em}
\plabel{$\blacktriangleright$}%
ことに天子の位置は尤も特別のものにて、\\
Particularly it is that the position of the Son of Heaven is the most special thing, and\\
これは實力あるものゝ手に歸したるが、\\
this (was the thing that) fell into the hands of those who have power,\\
天子になつても其家柄は第一流の貴族となるとは限らない。\\
even if (one) becomes the Son of Heaven, it is not necessary that his family becomes the lord of the first tier.

\vspace{1em}
\plabel{$\blacktriangleright$}%
唐太宗が天子になれるとき、\\
At the time when Emperor Taizong of Tang became the Son of Heaven,\\
貴族の系譜を調べさせたが、\\
(he) made (someone) investigate the genealogy of the lords, but\\
第一流の家柄は北方では博陵の崔氏、\\
as for the family of first tier, it is that in the north it was the family of Cui from Boling,\\
范陽の盧氏などにて、\\
(and) the family of Lu from Fanyang, etc., and\\
太宗の家は隴西の李氏で三流に位するといふことなりしも、\\
even though the family of Taizong became the thing (called) that position at a third-tier position as the family of Li from Longxi,\\
此家柄番附は、\\
as for this ranking list of families,\\
天子の威力でもこれを變更する事が出來なかつた。
even with the power of the Son of Heaven, the thing that (one) changes this thing was impossible.

\vspace{1em}
\plabel{$\blacktriangleright$}%
南朝に於ても王氏、謝氏などが天子の家柄よりも遙に重んぜられた。
Speaking of the Southern dynasties, also, the Family of Wang and the Family of Xie etc. was respected much more than the family of the Son of Heaven.

\vspace{1em}
\plabel{$\blacktriangleright$}%
是等は皆同階級の貴族の間で結婚をなし、\\
As for these, between lords of all the same ranks (they) accomplish marriage, and\\
それ等の團體が社會の中心を形成して、\\
these groups form the center of the society, and\\
最もよき官職は皆此仲間の占むる所となつた。\\
the best positions of office became the place that people among these occupy.

\prule

\plabel{$\blacktriangleright$}%
この貴族政治は唐末より五代までの過渡期に廢頽して、\\
This politics of lords becomes corrupt during the transition period from the end of the Tang dynasty and the Five Dynasties, and\\
これに代れるものが君主獨裁政治である。\\
the thing that substitutes this is the dictatorship of the monarch.

\vspace{1em}
\plabel{$\blacktriangleright$}%
貴族廢頽の結果、\\
(As) the result of the corruption of lords,\\
君主の位置と人民とが近接し來りて、\\
the position of the monarch and people come close,\\
高い官職につくのにも家柄としての特權がなくなり、\\
also for the thing of holding high office positions, it is that (there is) no privilege as a family, and\\
全く天子の權力によりて任命せらるゝ事となつた。\\
it all became the thing that is appointed by means of the power of the Son of Heaven.

\vspace{1em}
\plabel{$\blacktriangleright$}%
この制度は宋以後漸次發達して、\\
This system gradually develops after the Sond dynasty, and\\
明清時代は獨裁政治の完全なる形式をつくることゝなり、\\
in the Ming dynasty and the Qing dynasty, it becomes the thing that makes the complete form of the politics of dictatorship, and\\
國家に於ける凡ての權力の根本は天子一人これを有して、\\
with regards to the country, as for the root of all powers, the single person, the Son of Heaven, has it, and\\
他の如何なる大官も全權を有する事なく、\\
(there is) no other thing that all kind of important officers have full power, and\\
君主は決して如何なる官吏にも其職務の全權を委任せず、\\
the monarch by no means entrust the full power of his job to any kind of officers, and\\
從て官吏は其職務について完全なる責任を負ふ事なくして、\\
therefore, speaking of their job, (there is) no thing that officers take the full responsibility, and\\
君主一人がこれを負擔する事となつた。\\
it became the thing that the single person, the Son of Heaven, bear the burden of this.

\end{document}
